Negative Selection in the 20th Century

### 2020-05-16 why-negative-selection.Rmd
trivia

* Divide siblings regressions by own YOB, into early and late.
  - Use this to confirm the basic "selection decreasing" story
  - Actually almost no change.

* Plot average scores over time, as an intro graph. DONE
  - Can we work out how to plot selection effects on the "same scale"?
  - Simplest thing would be to use birth dates

@@

loadd(res_together)
n_regs <- as.double(nrow(res_together))
res_together %>% 
      mutate(
        term = pretty_names(term),
        term = fct_reorder(term, estimate),
        dep.var = recode(dep.var, 
          "n_children" = "N Children", "n_sibs" = "N Siblings")
      ) %>% 
      ggplot(aes(term, estimate, color = p.value < 0.05/{{n_regs}}, shape  = PCs)) + 
        geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) +
        my_hline +
        facet_wrap(vars(dep.var), scales = "free_x") +
        coord_flip() +
        scale_color_manual(values = pval_palette) +
        theme(legend.position = "bottom")
```

>>>>

* Divide siblings regressions by own YOB, into early and late.
  - Use this to confirm the basic "selection decreasing" story
  - Actually almost no change.
  - Overall, diffs between siblings and children regressions
    now look more like ascertainment bias than change over time.

* Plot average scores over time, as an intro graph. DONE
  - Can we work out how to plot selection effects on the "same scale"?
  - Simplest thing would be to use birth dates of children.

@@

loadd(res_together)
n_regs <- as.double(nrow(res_together))
res_together %>% 
      mutate(
        term = pretty_names(term),
        term = fct_reorder(term, estimate, order_abs),
        dep.var = recode(dep.var, 
          "n_children" = "N Children", "n_sibs" = "N Siblings")
      ) %>% 
      ggplot(aes(term, estimate, color = p.value < 0.05/{{n_regs}}, shape  = PCs)) + 
        geom_pointrange(aes(ymin = conf.low, ymax = conf.high)) +
        my_hline +
        facet_wrap(vars(dep.var), scales = "free_x") +
        coord_flip() +
        scale_color_manual(values = pval_palette) +
        theme(legend.position = "bottom")
```
